---
output: word_document
---

\begin{center}

R Homework 4

Fisher Ankney 

November 27th, 2018 

Statistics 5193 

\end{center}


#### Question 1

Manual Entry.

- Jim Scored an 80 and 75 on exam 1 and 2, Sam scored an 88 and 90, and Sally scored a 40 and a 100. Create a data frame called “you initials” for this data using the data editor in R. Give appropriate names to columns and print the data set to the console. Don’t forget to include all the code necessary to create the data set in your solution.

- Read the rownames help file. Use rownames to add appropriate row names to the data set and print the data set to the console. 

\hfill

```{r, eval=F}
fra <- data.frame()
fra <- edit(fra)

?row.names()

row.names(fra) <- c("Jim", "Sam", "Sally")
fra
```

```{r, echo=F}
`Exam 1` <- c(80, 88, 40)
`Exam 2` <- c(75, 90, 100)
fra <- data.frame(`Exam 1`, `Exam 2`)

row.names(fra) <- c("Jim", "Sam", "Sally")

fra
```

\hfill


#### Question 2

Go to https://fred.stlouisfed.org/series/DJIA and download the DJIA daily data from September as a comma delaminated excel data. Note you’ll have to change the dates in the upper right corner and click on CSV when downloading it. Delete any rows with missing data, if they exist. 

- Use read.csv(“DJIA.csv”, header = T) to import the data and print the first three rows to the console without creating an object in your workspace. 

-  Use read.table(“clipboard”, header = T) and the plot function to plot the data without ever saving the data in your workspace. Verify that the data set isn’t saved in your workspace using a function.

\hfill

```{r, eval = F}
head(read.csv("~/Downloads/DJIA.csv", header=T), n=3)
plot(read.table("clipboard", header = T))
ls()
```

```{r, echo=F}
head(read.csv("~/Downloads/DJIA.csv", header=T), n=3)
ls()
```


#### Question 3

Go to https://web.stanford.edu/~hastie/CASI_files/DATA/
- Provide a brief description of the data set
https://web.stanford.edu/~hastie/CASI_files/DATA/shakespeare.txt
 - Import the data directly from the URL with appropriate column names and construct a
plot of it. 

\hfill

"14,376 distinct words appeared once each in the canon,
4343 distinct words twice each; The canon has 884,647 total words,
counting repeats."

\hfill

```{r}
plot(
  read.csv(
    url("https://web.stanford.edu/~hastie/CASI_files/DATA/shakespeare.txt"),
    sep = " ", 
    header=T)
  )
```


\hfill


#### Question 4

Import the data set called “StudentDataExcelWorkbook” with column names. The data set is on the website. Save it as StudentData in your workspace, and print the first three rows to the
console.

\hfill

```{r}
library(readxl)
StudentData <- read_excel("~/Downloads/StudentData.xlsx")
StudentData[1:3,]
```


\hfill

### Question 5 

Import the data set called OrganicNigrogenDNA on the website. The row names identify the bacteria, and the columns identify the wheat plant (from smallest to largest). The number in row i and column j is the number of DNA copies for bacteria i from the j’th wheat plant. Import the data and save it as a data frame called DNA. The row names should be retained and the column names should be 1, 2, …, 9.

- Print the data for the first two bacteria.

- Get the 5 number summary and mean for data for each wheat plant (so 9 sets of summaries) and export the summaries to a text file. Upload the text file to the drop box. 

\hfill

```{r}
DNA <- read.csv("~/Downloads/OrganicNitrogenDNA.csv", row.names=1)
colnames(DNA) <- c(1:9)
DNA[1:2,]

?write.csv
write.csv(summary(DNA), file = "~/Documents/DNA_summary.txt")
```








