---
output: pdf_document
---
\begin{center}

R Homework 1

Fisher Ankney 

Statistics 5193 

\end{center}

### Question 1. 

Create an object whose name is your initials and has value 5.2. Add 5 to the object and print the
result.

\hfill

```{r}
FRA <- 5.2
FRA + 5
```

<br> 

### Question 2. 

Create an object called “n” that contains the numbers 1,2,3,4,5,6,7 and an object called fib that
contains the numbers 1, 1, 2, 3, 5, 8, 13, 21. Print the mean of fib.

\hfill

```{r}
n <- c(1,2,3,4,5,6,7)
fib <- c(1, 1, 2, 3, 5, 8, 13, 21)
mean(fib)
```

\hfill

### Question 3. 

Load the MASS package and read the help file. 

\hfill

```{r}
library(MASS)
help(package = "MASS")
```

\hfill

### Question 4.

Provide a short (few words) description of the UScrime data in the MASS package in R. 

\hfill

```{r}
data()
help(UScrime)
```

The Effect of Punishment Regimes on Crime Rates

\pagebreak

### Question 5. 

Consider the DDT data in the MASS package.

a. Provide a brief description of the data. 

\hfill

```{r}
help(DDT)
```

DDT in Kale

A numeric vector of 15 measurements by different laboratories of the pesticide DDT in kale, in ppm (parts per million) using the multiple pesticide residue measurement.

\hfill

b. Create an object called DDT.CI that contains a 95% confidence interval for the mean DDT
level. Use the formula $\bar{X} \pm 2 \frac{s}{\sqrt{n}}$

\hfill

```{r}
DDT.CI <- c(
            mean(DDT)-2*sd(DDT)/sqrt(length(DDT)),
            mean(DDT)+2*sd(DDT)/sqrt(length(DDT))
            )
DDT.CI
```

\hfill

c. Construct a histogram of the data using the hist() function.

\hfill

```{r}
hist(DDT)
```

