---
output: pdf_document
---

\begin{center}

R Homework 9

Fisher Ankney 

November 13th, 2018 

Statistics 5193 

\end{center}

### Question 1a

Functions: 

- Write a function called boot.mean that takes a sample from a vector called my.datawith replacement and returns the trimmed mean from the sampled vector.  For full credit

  - The inputs for the function are my.data and trim.perecent.
  
  - my.data should have no default value.
  
  - strim.percent has default value of 0.05 and is the percent        trimmed from each tail 

\hfill

```{r}
library(readxl)
StudentData <- read_excel("~/Documents/data_science/r_stat_5193/data/StudentData.xlsx")
```

\hfill

```{r}
boot.mean <- function(my.data, trim.percent = 0.05) {
  dat.sample <- sample(my.data, replace = T)
  mean(dat.sample, trim = trim.percent)
}
```

\hfill

### Question 1b

Get a bootstrapped sample 5% and 10% trimmed mean for the HSClass variable in the Social Media data set. 

\hfill

```{r}
# the use of attach is not recommended due to the convoluted nature of the 
# function, it reduces reproducibility, therefore I will reference the 
# dataframe in the suggested code

set.seed(1)
boot.mean(StudentData$HSClass)
boot.mean(StudentData$HSClass, trim.percent = .10)
```

\pagebreak

### Question 2a

For loop:

  - Write a for loop that runs boot.mean(HSClass) 10,000 times and save the means in a vector called my.boot.sample. Run the code set.seed(1) before your loop and print the mean and standard deviation of the vector to the console. 

\hfill

```{r}
my.boot.sample <- vector('double', length = 10000)

set.seed(1)
for (i in 1:10000) {
  my.boot.sample[i] <- boot.mean(StudentData$HSClass)
}

mean(my.boot.sample)
sd(my.boot.sample)
```

\hfill

### Question 2b

Construct a histogram of the 10,000 trimmed sample means with title “Trimmed Mean Sampling Distribution”. Use the probability=T option in the histogram. 

\hfill

```{r}
hist(my.boot.sample,
     probability = T,
     main = "Trimmed Mean Sampling Distribution")
```

\pagebreak


### Question 2c

Add a normal curve to the histogram that has mean equal to the mean and standard deviation computed in part a.

\hfill

```{r}
hist(my.boot.sample,
     probability = T,
     main = "Trimmed Mean Sampling Distribution")

curve(dnorm(x, mean = mean(my.boot.sample), sd = sd(my.boot.sample)),
      add = T)
```

\hfill

### Question 2d

Get the 2.5th percentile and the 97.5th percentile of my.boot.sample using the quantile function. Note: this is a 95% bootstrapped confidence interval of the 5% trimmed mean
for HS Class. Take STAT 5093 for more on the theory of bootstrapping. 

```{r}
quantile(my.boot.sample, c(0.025, 0.975))
```


\pagebreak

### Question 3a

```{r}
boot.ci <- function(my.data, trim.percent = 0.05, plot.it = T) {

# recreate boot.mean function
  boot.mean <- function(my.data, trim.percent = trim.percent) {
    dat.sample <- sample(my.data, replace = T)
    mean(dat.sample, trim = trim.percent)
  }

# create empty vector to store results
  my.boot.sample <- vector('double', length = 10000)

# loop
  for (i in 1:10000) {
    my.boot.sample[i] <- boot.mean(my.data, trim.percent = trim.percent)
  }

# save mean and sd for plotting
data.mean <- mean(my.boot.sample)
data.sd <- sd(my.boot.sample)

# return confidence interval
  print(quantile(my.boot.sample, c(0.025, 0.975)))
  
# conditional plot.it
  if (plot.it == T) {
     hist(my.boot.sample,
           probability = T,
           main = "Trimmed Mean Sampling Distribution")

     curve(dnorm(x, mean = data.mean, sd = data.sd), add = T)
     
  }
}

```

\pagebreak

### Question 3b

```{r}
# again, I'd rather specify the dataset instead of use attach()

set.seed(1)
boot.ci(StudentData$HSClass)
```

\pagebreak

### Question 3c

```{r}
# again, I'd rather specify the dataset instead of use attach()

set.seed(1)
boot.ci(StudentData$HSClass, trim.percent=.25)
axis(side=1, at=c(214.9068,417.5470 ),
        labels=F, col='red')
```

