---
output: pdf_document
---

\begin{center}

R Homework 11

Fisher Ankney 

November 27th, 2018 

Statistics 5193 

\end{center}

\hfill

### Question 1 


Generate data using the code “set.seed(1)” and “x<-rlnorm(50, meanlog=0, sdlog=2)”.
Construct a boxplot of the data that is

- red and has title “Boxplot of lognormal data”

- has a tick mark for the median with the value of the median printed on the left side of
the y axis.

- Identifies outliers as being greater than Q3+ 3*(Q3 – Q1), plots outliers with a “+”, and
depicts the outlier cutoff with a dashed red line.

- Has a legend that reads “+ outlier”

- Draws a tick mark for each observation on the right axis. 

\hfill

```{r}
set.seed(1)

x <- rlnorm(50, meanlog = 0,sdlog = 2)

boxplot(x,col = "red",
        main="Boxplot of Lognormal Data",
        range=3, 
        yaxt='n',
        pch=3)

summary <-boxplot.stats(x)  

axis(2,at=summary$stats[3])  

outlier<-summary$stats[4] + 3*(summary$stats[4] - summary$stats[2])

abline(h=outlier, col ="red", lty =2)

legend("topleft", legend="outlier", pch ="+", inset=0.05 )

axis(4,at=x, label=FALSE)
```

\pagebreak

### Question 2

For the student data, make side by side boxplots of FBtime by Pinterest and Gender. There should be four boxes – the first 2 are females and the second 2 are males. Specific details are:

- The female boxes should be pink and the male boxes blue

- Each box should be labeled either “Pinterest” or “No Pinterest”

- You must have the y axis labeled and have a title

- There should be a legend that indicates Female and Male with a pink and blue box, respectively. Hint: see the fill option

\hfill

```{r}
library(readxl)
StudentData <- read_excel("/Users/fisher/Documents/data_science/r_stat_5193/data/StudentData.xlsx")
```

```{r}

boxplot(StudentData$Fbtime ~ StudentData$Pinterest*StudentData$Gender, 
        col = c('pink', 'pink', 'blue', 'blue'), 
        names = c('No Pinterest', 'Pinterest', 'No Pinterest', 'Pinterest'),
        ylab = 'FB Time',
        main = 'FB time vs. Pinterest by Gender'
)

legend('topleft', legend = c('Female', 'Male'), fill = c('pink', 'blue'))
```

\pagebreak


### Question 3 


Get the medians of the 4 groups above and the 5% trimmed means of the four groups above using aggregate function.

\hfill

```{r}
aggregate(StudentData$Fbtime,
          by = list(pinterest = StudentData$Pinterest,
                    gender = StudentData$Gender),
          FUN = median)

ag_mean <- function(x) {
  mean(x, trim = 0.05)
}

aggregate(StudentData$Fbtime,
          by = list(pinterest = StudentData$Pinterest,
                    gender = StudentData$Gender),
          FUN = ag_mean)
```

\pagebreak

### Question 4

Create a dotplot of murder rates by state using the USArrests data. Make sure to order the data by murder rate and provide a title and state names. 

\hfill

```{r}
ordered <- USArrests[order(USArrests$Murder),]

dotchart(ordered$Murder, labels = row.names(ordered),
         main = "Murder Rate by State")
```


