---
output: pdf_document
---

\begin{center}

R Homework 11

Fisher Ankney 

November 27th, 2018 

Statistics 5193 

\end{center}

\hfill

*Note: this document was created using R Markdown.

\hfill

### Question 1 


. Create a 2 x 2 table of gender and pinterest with gender on the rows and Pinterest on
the Columns. Print it to the console.


```{r}
library(readxl)
StudentData <- read_excel("/Users/fisher/Documents/data_science/r_stat_5193/data/StudentData.xlsx")
```

```{r}
ex_table <- table(StudentData$Gender, StudentData$Pinterest)
ex_table
```

\hfill

### Question 1b

```{r}
ex_prop_table <- prop.table(margin.table(ex_table, 1:2), 1)
ex_prop_table
```

\pagebreak


### Question 1c

```{r}
resid(chisq.test(ex_table[,2]))
```

More women have pinterest than is expected, and less men have pinterest than is expected, if the expectation is that gender has no effect on pinterest use. 

\hfill

### Question 1d

```{r}
barplot(t(ex_table),
        beside = T, 
        names = c('Female', 'Male'),
        col = c('slateblue', 'firebrick', 'slateblue', 'firebrick'))

legend('topright',
       title = 'Has Pinterest?',
       legend = c('No', 'Yes'),
       fill = c('slateblue', 'firebrick'))

```


\pagebreak


### Question 1e


```{r}
barplot(t(ex_table),
        main = 'Pinterest Depends on Gender (p = 0.03397)',
        beside = T, 
        names = c('Female', 'Male'),
        col = c('slateblue', 'firebrick', 'slateblue', 'firebrick'))

legend('topright',
       title = 'Has Pinterest?',
       legend = c('No', 'Yes'),
       fill = c('slateblue', 'firebrick'))
```

\pagebreak


### Question 2a
```{r}
class_surv <- apply(Titanic, c(1,4), sum)

library(vcd)
mosaic(class_surv, legend = T, gp = shading_max)
```

\hfill

Yes, survival rate depends on class, with a p-value of $< 2.22*10 ^{-16}$

\pagebreak

### Question 3 
```{r}
sex_surv <- apply(Titanic, c(2,4), sum)
mosaic(sex_surv, legend = T, gp = shading_max)
```

Yes, survival rate does depend on gender, with a p-value $< 2.22 * 10^{-16}$.


\pagebreak

### Question 4
```{r}
age_surv <- apply(Titanic, c(3,4), sum)
mosaic(age_surv, legend = T, gp = shading_max)
```

Yes, survival rate does depend on age, with a p-value $< 2.22 * 10^{-16}$.
