---
output: pdf_document
---

\begin{center}

R Homework 13

Fisher Ankney 

December 4th, 2018 

Statistics 5193 

\end{center}

\hfill

### Question 1a

Consider Student Data - Class size and snapchat. Get a 95% students-T based confidence interval for the mean high school class size and interpret it.

\hfill

```{r}
library(readxl)
StudentData <- read_excel("/Users/fisher/Documents/data_science/r_stat_5193/data/StudentData.xlsx")

t.test(StudentData$HSClass)
```

\hfill

We can be 95% confident that the mean high school class size is between 216.73 and 426.07 students. 

\pagebreak

### Question 1b

Get side by side boxplots for high school class among Snapchat users and non- Snapchat
users.

\hfill

```{r}
boxplot(StudentData$HSClass~StudentData$Snapchat)
```

\pagebreak

### Question 1c

Get a p-value for testing the null hypothesis that the mean high school class size is smaller among students who do not have a Snapchat account and interpret it. Assume unequal variances and that data are normally distributed.

\hfill

```{r}
hs_no_snap <- StudentData[StudentData$Snapchat == 'N',]$HSClass
hs_yes_snap <- StudentData[StudentData$Snapchat == 'Y',]$HSClass

t.test(hs_no_snap, hs_yes_snap, var.equal = F, alternative = 'less')
```

\hfill

Assuming a confidence 95%, there is sufficient evidence to suggest that the mean high school size is smaller among students who do not have snapchat. The p-value is 0.049, this barely signifying significance. 

\pagebreak 

### Question 1d

 Get a 90% confidence interval for the difference in mean high school class size among Snapchat vs. non- Snapchat users and interpret it. Assume unequal variances and that data are normally distributed.

\hfill

```{r}
t.test(StudentData$HSClass ~ StudentData$Snapchat, var.equal = F, conf.level = .9)
```

\hfill

We're 90% confident that the difference in mean high school class size is between -312.39 and -0.59 students. Meaning that students who do have snapchat, have an mean high school class size that is between 0.59 and 312.39 students larger than their counterparts that do not have snapchat. 
\pagebreak

### Question 2a


Consider the USArrests data - Construct a plot of Assault vs. Murder with Assault on the x axis and draw the least squares regression line on the plot.

\hfill

```{r}
plot(USArrests$Murder ~ USArrests$Assault)
lines(abline(lm(USArrests$Murder ~ USArrests$Assault)))
```

\pagebreak

### Question 2b

Are assault and murder rates independent? Use a p-value to justify your answer?

\hfill

```{r}
cor.test(USArrests$Murder, USArrests$Assault)
```

\hfill

Assault and murder rates are not independent, they have a correlation coefficient of 0.8 (high positive correlation), and a pvalue of $< 0.005$. 
\hfill

### Question 2c

Read the help file for predict.lm. Get a 95% prediction interval for the murder rate of a state that has an assault rate of 151 (Oklahoma’s) using the predict function.

\hfill

```{r}
?predict.lm

assault_murder <- lm(Murder ~ Assault, data = USArrests)

new_data <- data.frame(Assault = 151)

predict.lm(assault_murder, new_data, interval='prediction')
```

\pagebreak


### Question 2d 

Add lines representing the 95% prediction intervals. That is, get lower limits and upper limits for the 95% prediction intervals as a function of x and add them to the plot.

\hfill

```{r}
pred_int <- predict.lm(assault_murder, newdata = data.frame(Assault = 50:400), interval = 'prediction')
new_x <- seq(50, 400, by = 1)

# original plot
plot(USArrests$Murder ~ USArrests$Assault)
lines(abline(lm(USArrests$Murder ~ USArrests$Assault)))

# prediction interval
lines(new_x, pred_int[,2], col = 'orange', lty = 2)
lines(new_x, pred_int[,3], col = 'orange', lty = 2)
```

