---
output: pdf_document
---
R Midterm Exam

Fisher Ankney 

November 15th, 2018 

Statistics 5193 

*Note: this document was created using R Markdown, as usual.


## Question 1

```{r}
rm(list = ls())
ls()
```

\hfill

### Question 2

```{r, echo = F}
library(readxl)
FRA <- read_excel("~/Documents/data_science/r_stat_5193/data/StudentData.xlsx")
FRA <- as.data.frame(FRA)
row.names(FRA) <- 1:35
```

```{r, eval = F}
FRA <- read.table("clipboard", header = T))
row.names(FRA) <- 1:35
```

\hfill

### Question 3 
```{r}
FRA[c(3,5),]
```


\hfill

### Question 4

```{r}
FRA_sort <- FRA[order(FRA$Gender, FRA$Introvert),]
FRA_sort[1:3,]
```

\hfill

### Question 5

```{r}
small_index <- FRA$HSClass <= 100
large_index <- FRA$HSClass > 100

HSClass.cat <- vector('character', length(35))

HSClass.cat[small_index] <- 'Small'
HSClass.cat[large_index] <- 'Large'

summary(HSClass.cat)
```

\hfill

### Question 6

```{r}
HSClass.cat <- factor(HSClass.cat, ordered = T, levels = c('Small', 'Large'))
summary(HSClass.cat)
```

\pagebreak

### Question 7 

```{r}
Texts <- matrix(FRA$TxtSent, FRA$TxtRec, nrow = 35, ncol = 2)

summary(Texts[,1])
mean(Texts[,1])

summary(Texts[,2])
mean(Texts[,2])
```

\pagebreak

### Question 8 

```{r}
gender <- as.factor(FRA$Gender)

plot(FRA$TxtRec, FRA$TxtSent, 
     xlab = 'Texts Recieved',
     ylab = 'Texts Sent', 
     pch = c(5,1)[gender],
     col = c('violet', 'slateblue')[gender])
```

\pagebreak

### Question 9

```{r}
plot(FRA$TxtRec, FRA$TxtSent, 
     xlab = 'Texts Recieved',
     ylab = 'Texts Sent', 
     pch = c(5,1)[gender],
     col = c('violet', 'slateblue')[gender])

popular_guy <- FRA[FRA$TxtSent == 100 & FRA$TxtRec == 200,]


text(popular_guy$TxtRec,
     popular_guy$TxtSent,
     label = "He's Popular?",
     pos = 2
      )
```


\pagebreak


### Question 10 

```{r}
plot(FRA$TxtRec, FRA$TxtSent, 
     xlab = 'Texts Recieved',
     ylab = 'Texts Sent', 
     pch = c(5,1)[gender],
     col = c('violet', 'slateblue')[gender])

popular_guy <- FRA[FRA$TxtSent == 100 & FRA$TxtRec == 200,]


text(popular_guy$TxtRec,
     popular_guy$TxtSent,
     label = "He's Popular?",
     pos = 2
      )

title(main = "Texting vs. Gender", 
      cex.main = 2,
      col.main = 'blue')
```

\pagebreak


### Question 11

```{r}
plot(FRA$TxtRec, FRA$TxtSent, 
     xlab = 'Texts Recieved',
     ylab = 'Texts Sent', 
     pch = c(5,1)[gender],
     col = c('violet', 'slateblue')[gender])

popular_guy <- FRA[FRA$TxtSent == 100 & FRA$TxtRec == 200,]


text(popular_guy$TxtRec,
     popular_guy$TxtSent,
     label = "He's Popular?",
     pos = 2
      )

title(main = "Texting vs. Gender", 
      cex.main = 2,
      col.main = 'blue')

legend('bottomright', 
       c('male','female'),
       col=c('slateblue', 'violet'),
       pch=c(1,5),
       inset = 0.05)
```


\pagebreak


### Quetion 12

```{r}
males <- FRA[FRA$Gender == 'M',]
females <- FRA[FRA$Gender == 'F',]

male_reg <- lm(males$TxtRec ~ males$TxtSent)
female_reg <- lm(females$TxtRec ~ females$TxtSent)

plot(FRA$TxtRec, FRA$TxtSent, 
     xlab = 'Texts Recieved',
     ylab = 'Texts Sent', 
     pch = c(5,1)[gender],
     col = c('violet', 'slateblue')[gender])

popular_guy <- FRA[FRA$TxtSent == 100 & FRA$TxtRec == 200,]


text(popular_guy$TxtRec,
     popular_guy$TxtSent,
     label = "He's Popular?",
     pos = 2
      )

title(main = "Texting vs. Gender", 
      cex.main = 2,
      col.main = 'blue')

legend('bottomright', 
       c('male','female'),
       col=c('slateblue', 'violet'),
       pch=c(1,5),
       inset = 0.05)

lines(abline(male_reg, col = 'slateblue'))
lines(abline(female_reg, col = 'violet'))
```

\pagebreak


### Question 13

```{r}
binom_sample <- rbinom(1000, size = 50, prob = .5)

hist(binom_sample, probability = T)

curve(dnorm(x,
            mean(binom_sample),
            sd(binom_sample)),
      add = T,
      col='firebrick')
```


\pagebreak


### Question 14 

```{r}
of.age <- function(name, age = 21) {

if (age >= 21) {
    output <- paste(substitute(name), 'is at least 21')
    return(output)
  } else {
    output <- paste(substitute(name), 'is not at least 21')
    return(output)
  }
  
}

of.age(Fisher, 25)
```

\pagebreak

### Question 15
```{r}
data <- 0:99

results_vector <- vector('double', length(1000))

for (i in 1:1000) {
  results_vector[i] <- mean(sample(data, 10, replace = T))
}

hist(results_vector, 
     main = 'The distribution of the sample mean')
```

