---
output: pdf_document
---

### Fisher Ankney
### October 18th, 2018
### Statistics 5193

*Note: this document was created using R Markdown. Dr. Habiger has confirmed that this is an acceptable way to turn in each assignment. 

R code input will be of the form:
```{r, eval=F}
"this is R code input"
``` 

R code output will be of the form 
```{r, echo=F}
"this is R code output"
``` 


#### Question 1a.

```{r, message=F}
library(readxl)
student_data <- read_excel("~/Downloads/StudentData.xlsx")
```

```{r}
text_sent <- student_data$TxtSent
text_recieve <- student_data$TxtRec
facebook_time <- student_data$Fbtime
```

\hfill

### Question 1b. 

```{r}
text_sent[c(1,3)]
text_recieve[c(1,3)]
facebook_time[c(1,3)]
```

\hfill

### Question 1c.
```{r}
storage.mode(text_sent)
class(text_sent)
```

\pagebreak

### Question 2a.
```{r}
id_num <- 1:35
sm <- matrix(c(text_sent, text_recieve, facebook_time), nrow=35, ncol=3)
colnames(sm) <- c("text_sent", "text_recieved", "facebook_time")
rownames(sm) <- id_num

sm[4,]
```


\hfill

### Question 2b. 
```{r}
is.matrix(sm)
dim(sm)
```

\hfill

### Question 2c.
```{r}
male <- student_data$Gender == "M"
female <- student_data$Gender == "F"

median(student_data[male, ]$Fbtime)
median(student_data[female, ]$Fbtime)
```

\hfill

### Question 2d. 
median and mean for difference between text sent and text recieved
```{r}
text_diff <- text_sent - text_recieve

mean(text_diff)
median(text_diff)
```


\hfill

### Question 3.
```{r}
SM.Array <- as.array(sm)
SM.Array[c(1,35),]
```



\hfill

### Question 4.

```{r}
help(mean)
help(letters)
```

The mean function only works for objects that are of the storage mode numeric / logical vectors, dates, date-times, and time intervals. Letters are characters, and not on this list of viable data types. 