---
output: pdf_document
---
### Homework 3
### Fisher Ankney
### Stat 5193

*Note: this document was created using R Markdown. Dr. Habiger has confirmed that this is an acceptable way to turn in each assignment. 

R code input will be of the form:
```{r, eval=F}
"this is R code input"
``` 

R code output will be of the form 
```{r, echo=F}
"this is R code output"
``` 


#### Question 1a
```{r}
library(readxl)
stud_dat <- read_excel("~/Downloads/StudentData.xlsx")

text.sent <- stud_dat$TxtSent
Fb.time <- stud_dat$Fbtime
gender <- stud_dat$Gender

mode(text.sent)
mode(Fb.time)
mode(gender)
```

\hfill

#### Question 1b

```{r}
fra <- data.frame(text.sent, Fb.time, gender)
fra[1:3,]
```


\pagebreak 

#### Question 1c

```{r}
str(fra)

fra$gender
"no"
```

\hfill

#### Question 1d
```{r}
summary(fra)

# male prop
sum(fra$gender == "M") / length(fra$gender)
```


\pagebreak 

#### Question 1e
```{r}
boxplot(fra$Fb.time~fra$gender)
```

\hfill

#### Question 2a
```{r}
set.seed(1)
x <- rpois(25,1)
x.f <- factor(x, order=T, levels = c(0,1,2,3,4,5))

x.f
```

\hfill


#### Question 2b
```{r}
help(table)
"combination of factor"

plot(table(x.f))
```


\hfill


#### Question 3a

```{r}
fra <- list(first.name = "Fisher Ankney", matrix(c(1,0,0,1), nrow=2, ncol=2), summary(fra))
fra
```

\hfill

#### Question 3b

```{r}
fra <- fra[1:2]
fra[[2]]
```

